Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-04-05 thesis/acknowledgments.tex
started writing

>>>>

To my wife Ellen, who moved across the country for me to N.Y.C. and has put up
with so much over the past six years just so that I could pursue my dream.

I want to thank all of the other graduate students at Columbia that I have overlapped
with over the years. This includes especially Sarah, Steven, Dan, Jeff, Adrian,
Munier, Andrea, Alejandro, and Susan. \textit{a little more here}

Thank you to everyone I have met in the NYC climbing community who have collectively
help keep me sane throughout my time in graduate school. Over the past few years
I have learned the importance of a proper work-life balance, and climbing has helped
me keep that balance (... maybe a bit too well...). Thank you especially to my
regular climbing partners -- Daniel, Hunter, Dennis, and Lauren A. -- who I've trusted
with my life countless times, and the handful of other astronomer-climbers that I've
climbed with throughout graduate school (Jeff, Matt, Lauren A., Dan D'Orazio,
Dan Foreman-Mackey, and Andrea).
